%---
\section{Configuration Control}


%---
\subsection{WBS Control Plan}
The Technical Coordinators are responsible for carrying out the configuration control plan per the process for managing changes to said plan, laid out by the project controls team which worked with the Collaboration to develop and maintain the WBS. The WBS contains data from the control systems and is the basis for information entered into the Primavera P6 system. This WBS provides the essential earned value information needed for management control of the project and maintains the database for progress reporting. The system integrates the cost and schedule baselines and provides the tools to monitor project performance. The technical coordinators will keep track of project related documentation, act as a point of contact between the L1 Managers and the project controls team, ensure appropriate approvals are received, and notify the collaborators when changes and updates have been made. The changes themselves will be vetted by the Technical Board before implementation into official documentation.

%---
\subsection{Change Control Plan}
The project has implemented a change control plan that requires a Change Control Board (CCB) to review any changes that impact the projects scope, cost and/or schedule. The process promotes orderly evolution from the baseline design, and ensures that the effect of changes on cost, schedule, and technical scope performance are properly evaluated and documented by project management and the CCB. A Baseline Change Request (BCR) must be initiated when there will be an impact on any of the cost, schedule, or scope baselines. Thresholds for determining the BCR approval level during project execution are still being defined but will be in place before the start of the project.

%---
\subsection{Document Control Plan}
The aim of the document control plan is to control the storage of documents and important historical data and information. The plan establishes a methodology for the creation, update, and arrangement of documents. This plan will be evaluated annually and updated as necessary to ensure continuous improvement.  Project collaborators will be responsible for the creation and storage of documents and for completion of document profiles.  The Project Scientists will act as the project document librarians, keeping track of versioning.  All documents will be stored in a permanent repository with access to all collaborators.  When a document is ready for replacement by a new version, the Project Scientists will ensure the new version abides by the project standards for that document type.  
%
