%%\documentclass[aps,twocolumn]{article}%
%%\usepackage{graphicx}
%%\begin{document}
\label{sec:PE}
\section {PhotoElectronics}

After the completion of the first motherboard, equipped with 25 PDMs containing each 24 single dose SiPM's, the DarkSide collaboration moved to the construction of a second Motherboard, equipped with triple dose SiPMs. At the moment half of the SiPM tiles have been already mounted and successfully tested in liquid nitrogen. A 3 months delay in the delivery of the remaining SiPMs from the FBK company, Trento, Italy, reflected in a delay of the motherboard production schedule. The remaining triple dose SiPMs were just shipped by FBK. We are confident to finalize this motherboard by the end of April.\\
The prototype boards of the opto-link system (optical driver and optical receiver board) have been just produced. The optical receiver board (32 channels) was successfully tested, while the optical driver board (25 channels) is at the moment under test. \\
The next step in the photo-electronics schedule is the production of about 400 PDMs for the 1-ton prototype. These SiPMs will be produced by the LFoundry company, Avezzano, Italy: the first run is expected by the end of May. A first engineering run, finalized in September 2018 and tested shortly after, showed the capability of the silicon foundry to implement the FBK technology: the produced SiPM's showed a good performance both at room temperature and in liquid nitrogen. A second LFoundry engineering run, presently ongoing, is devoted to the true silicon via's (TSV) making. This post-production rework requires the use of a thin layer (few hundreds of microns) of material on the top of the SiPM's. For the first time fused silica will replace glass, showing a too high level of radioactivity.\\
As far as the procurement of the equipment for the \DSk\ clean room massive production is concerned, the cryogenic probe tender was just approved by the INFN Executive Board and the flip-chip bonder tender will follow in few weeks. \\
The \DSk\ SiPM packaging foresees the production of more than 10,000 PDM's in 2.5 years. 
This remarkable effort requires a large clean room, relying on cutting edge technology equipment and 
trained personnel.\\
The Tecnopolo's (AQ) clean room, selected as  \DSk\ SiPM packaging facility, has a
large area, already available, exceeding 700\,m$^{2}$. At the moment this space is being refurbished and will comfortably host 
the needed equipment and the personnel. 
This facility will be rented by INFN and GSSI:  an agreement for the use of the Tecnopolo clean room has been already signed. 
The tender for the cryogenic probe procurement  
has been finalized and the approval for the  flip-chip bonder tender is expected to come in few weeks. 
%({\it eugenio.scapparone@bo.infn.it})  \\

%%\subsection {Introduction}
